Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Toward Better Low-Rate Deep Learning-Based CSI Feedback: A Test Channel-Based Approach
✅ Citation-rich Zone-Specific CSI Feedback for Massive MIMO: A Situation-Aware Deep Learning Approach

@@

>>>>

\cite{wang2024better} introduces a novel test channel-based quantization module (TCQM) that addresses critical limitations in DL-based CSI feedback systems.
\cite{zhang2024zone} proposes a novel zone-specific deep learning approach for CSI feedback in massive MIMO systems. The key innovation partitions the coverage area into spatial zones with distinct channel characteristics, training specialized autoencoders for each zone.

@@

	\bibitem{wang2024better} 
	J. Wang et al., 
	``Toward Better Low-Rate DL-Based CSI Feedback: A Test Channel-Based Approach,'' 
	\textit{IEEE Trans. Wireless Commun.}, 
	vol. 23, no. 5, pp. 3210-3224, May 2024.

	\bibitem{zhang2024zone} 
	Y. Zhang, A. Alkhateeb, 
	``Zone-Specific CSI Feedback for Massive MIMO,'' 
	\textit{IEEE Wireless Commun. Lett.}, 
	early access, 2024.
